A Comparison of Graph Processing Systems

### 2020-08-24 documentation/paper/sections/results/results.tex
distributed plots

\subsection{Single-source Shortest-paths}
\autoref{fig:singleNodeSSSP} shows the average calculation times (time without initialization overhead), execution time and the normalized overhead for SSSP on the different frameworks. In these figures, Galois with 96 threads is shown. We show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}[t!]
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{Calculation times for SSSP on a single node}
		\label{fig:singleNodeSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{Execution times for SSSP on a single node}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_overheadTimeNormalized.png}
		\caption{Overhead time (execution time - calculation time) normalized by the graph size in million edges}
		\label{fig:singleNodeSSSP_overheadNormalized}
	\end{subfigure}
	\caption{Average times on a single computation node, black bars represent one standard deviation in our testing.}
	\label{fig:singleNodeSSSP}
\end{figure*}

\subsection{Breadth-first search}
In these figures, Galois with 96 threads is shown. Again, we show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_calcTime.png}
		\caption{Calculation times for BFS on a single node}
		\label{fig:singleNodeBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_execTime.png}
		\caption{Execution times for BFS on a single node}
		\label{fig:singleNodeBFS_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_overheadTimeNormalized.png}
		\caption{Overhead time (execution time - calculation time) normalized by the graph size in million edges}
		\label{fig:singleNodeBFS_overheadNormalized}
	\end{subfigure}

@@

>>>>

\subsection{Single-source Shortest-paths}
\autoref{fig:singleNodeSSSP} shows the average calculation times (time without initialization overhead), execution time and the normalized overhead for SSSP on the different frameworks. In these figures, Galois with 96 threads is shown. We show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}[t!]
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_calcTime.png}
		\caption{Calculation times for SSSP on a single node}
		\label{fig:singleNodeSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_execTime.png}
		\caption{Execution times for SSSP on a single node}
		\label{fig:singleNodeSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeSSSP_overheadTimeNormalized.png}
		\caption{Overhead time normalized by the graph size in million edges}
		\label{fig:singleNodeSSSP_overheadNormalized}
	\end{subfigure}
	\caption{Average times on a single computation node, black bars represent one standard deviation in our testing.}
	\label{fig:singleNodeSSSP}
\end{figure*}

\begin{figure*}[t!]
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_calcTime.png}
		\caption{Calculation times for distributed SSSP}
		\label{fig:distributedSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_execTime.png}
		\caption{Execution times for distributed SSSP}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_overheadTimeNormalized.png}
		\caption{Overhead time normalized by the graph size in million edges}
		\label{fig:distributedSSSP_overheadNormalized}
	\end{subfigure}
	\caption{Average times on the distributed cluster, black bars represent one standard deviation in our testing.}
	\label{fig:distributedSSSP}
\end{figure*}

\subsection{Breadth-first search}
In these figures, Galois with 96 threads is shown. Again, we show the impact of Galois' thread count in \autoref{sec:galois_speedup}.
\begin{figure*}
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_calcTime.png}
		\caption{Calculation times for BFS on a single node}
		\label{fig:singleNodeBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_execTime.png}
		\caption{Execution times for BFS on a single node}
		\label{fig:singleNodeBFS_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_overheadTimeNormalized.png}
		\caption{Overhead time normalized by the graph size in million edges}
		\label{fig:singleNodeBFS_overheadNormalized}
	\end{subfigure}

@@

\begin{figure*}
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_calcTime.png}
		\caption{Calculation times for distributed BFS}
		\label{fig:distributedBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_execTime.png}
		\caption{Execution times for distributed BFS}
		\label{fig:distributedBFS_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.3\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_overheadTimeNormalized.png}
		\caption{Overhead time normalized by the graph size in million edges}
		\label{fig:distributedBFS_overheadNormalized}
	\end{subfigure}

	\caption{Average times on the distributed cluster, black bars represent one standard deviation in our testing}
\end{figure*}

### 2020-08-24 documentation/paper/sections/testingMethods.tex
distributed plots

\subsection{Hardware and Software}
For testing all systems we used 5 machines with 96 CPU cores each (48 physical) and 256 GB of RAM. One of those machines was only used as part of the distributed cluster, since it only has 128 GB of RAM.
All servers were running Ubuntu 19.x.
Setup of each framework was performed according to our provided installation guides.

@@

For the \emph{calculation time}, we tried to extract only the time the framework actually executed the algorithm. We came up with the following:
\begin{itemize}
	\item For Galois, we resulted to extracting console log time stamps. Galois outputs \texttt{Reading graph complete.}. Calculation time is the time from this output to the end of execution.
	\item Polymer outputs the name of the algorithm followed by a measured time.
	\item Gemini outputs a line \texttt{exec\_time=x}, which was used to measure the calculation time. 
	\item Ligra outputs a measured time with \texttt{Running time : x}.
	\item Giraph has built in timers for the iterations (supersteps) which we used to extract the computation time.
\end{itemize}
Each test case consisting of graph, framework and algorithm was run 10 times, allowing us to smooth slight variations in the measured times.

@@

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PageRank in push and pull modes), we included the alternatives in our testing. 
\autoref{tbl:algorithms} shows the tested algorithms in detail.
\newcommand{\txtdag}{\textsuperscript{\textdagger}}
\begin{table}
	\centering
	\begin{tabularx}{0.9\columnwidth}{cYYYYY}
		\bf{Algorithm}&Galois&Gemini&Giraph&Ligra&Polymer\\\hline
		PageRank&$\Delta$Push, $\Delta$Pull&&&&\\
		SSSP&?, Push, Pull&&&&\\
		BFS&Yes&&*&&\\
		\hline
	\end{tabularx}
	\caption{Tested algorithms of the frameworks}
	\label{tbl:algorithms}

>>>>

\subsection{Hardware and Software}
For testing all systems we used 5 machines with 96 CPU cores each (48 physical) and 256 GB of RAM. One of those machines was only used as part of the distributed cluster, since it only has 128 GB of RAM.
All five machines were running Ubuntu 18.04.2 LTS.
Setup of each framework was performed according to our provided installation guides\footnote{The setup guides are available at \url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}.

@@

For the \emph{calculation time}, we tried to extract only the time the framework actually executed the algorithm. We came up with the following:
\begin{itemize}
	\item For Galois, we resulted to extracting console log time stamps. Galois outputs \texttt{Reading graph complete.}. Calculation time is the time from this output to the end of execution.

	We know that this is not the most realiable way for measuring the calculation times. 
	Not only due to unavoidable buffering in the console output we expect the measured time to be larger than the actual.
	First, it is not clear that all initialization is in fact complete after reading the graph. Second, we include time that is used for cleanup after calculation in the measurement.

	\item Polymer outputs the name of the algorithm followed by an internally measured time.

	\item Gemini outputs a line \texttt{exec\_time=x}, which was used to measure the calculation time.

	\item Ligra outputs its time measurement with \texttt{Running time : x}.

	\item Giraph has built in timers for the iterations (supersteps) which we summed up to extract the computation time.
\end{itemize}
Furthermore, the \emph{overhead} is the time difference between execution time and calculation time.

Each test case consisting of graph, framework and algorithm was run 10 times, allowing us to smooth slight variations in the measured times.
Later on, we provide the mean values of the individual times as well as the standard deviation where meaningful.

@@

\subsection{Algorithms}
The three problems Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) were used to benchmark framework with every graph.
For frameworks that support multiple implementations (e.g. PageRank in push and pull modes), we included the alternatives in our testing. 
\autoref{tbl:algorithms} shows the tested algorithms in detail.

\newcommand{\txtdag}{\textsuperscript{\textdagger}}
\begin{table}
TODO
	\centering
	\begin{tabularx}{0.9\columnwidth}{cYYYYY}
		\bf{Algorithm}&Galois&Gemini&Giraph&Ligra&Polymer\\\hline
		PageRank&$\Delta$Push, $\Delta$Pull&&&&\\
		SSSP&?, Push, Pull&&&&\\
		BFS&Yes&&*&&\\
		\hline
	\end{tabularx}
	\caption{Tested algorithms of the frameworks}
	\label{tbl:algorithms}
